Gastro-intestinal transmission and colonisation of _Clostridioides difficile_ and antimicrobial-resistant bacteria in healthcare settings -- calibration of an agent-based model

### 2025-10-07 paper/paper.qmd
tune and sens now use side-room-delay-mean

param_units <- c("toilet-frequenting-rate" = "times per day",
                 "toilet-cleaning-rate" = "times per day",
                 "toilet-contamination-effect" = "",
                 "toilet-cleaning-effect" = "",
                 "community-colonisation-rate" = "percentage of patients",
                 "antibiotic-prescription-rate" = "percentage of admissions",
                 "antibiotic-effect" = "relative risk",
                 "random-colonisation" = "cases per 10,000 bed days",
                 "proportion-redistributed" = "proportion of patients")

param_names <- c("toilet-frequenting-rate" = "Toilet frequenting rate",
                 "toilet-cleaning-rate" = "Toilet cleaning rate",
                 "toilet-contamination-effect" = "Toilet contamination effect",
                 "toilet-cleaning-effect" = "Toilet cleaning effect",
                 "community-colonisation-rate" = "Community colonisation rate",
                 "antibiotic-prescription-rate" = "Antibiotic prescription rate",
                 "antibiotic-effect" = "Antibiotic effect",
                 "random-colonisation" = "Random colonisation",
                 "proportion-redistributed" = "Proportion redistributed")

@@

```{r fig-sensitivity-analysis, include=TRUE, eval=TRUE}
#| echo: false
#| fig-cap: "Sensitivity analysis of the model to changes in key infection control parameters. The y axis shows the total number of nosocomial infections during the outbreak period. Antimicrobial prescription rate represents the percentage of patients that were administered an antimicrobial during their admission. Proportion redistributed represents the proportion of infected patients that were moved to a single-occupancy room (lower values represent fewer patients being moved). Toilet cleaning effect represents the effectiveness of cleaning in reducing toilet contamination (100% = complete removal of contamination; 0% = no cleaning effect). Toilet cleaning rate represents the number of times toilets were cleaned per day, on average."
list(
  abx_prescription_rate    = sens_abx_prescription_outbreak_cases,
  proportion_redistributed = sens_prop_redist_outbreak_cases,
  toilet_cleaning_rate     = sens_toilet_cleaning_rate_outbreak_cases,
  toilet_cleaning_effect   = sens_toilet_cleaning_effect_outbreak_cases
) %>%
  bind_rows() %>% 
  pivot_longer(
    cols = starts_with("c-"),
    names_to = "param",
    values_drop_na = TRUE
  ) %>% 
  group_by(param, value) %>% 
  summarise(
    mean_cases = mean(`outbreak-cases`),
    sd_cases   = sd(`outbreak-cases`),
    .groups    = "keep"
  ) %>% 
  mutate(
    # convert antibiotic prescription rate to 0-100 scale, leave others unchanged
    # value = if_else(param == "c-antibiotic-prescription-rate", value * 100, value),
    param = case_when(
      param == "c-antibiotic-prescription-rate" ~ "Antimicrobial prescription rate",
      param == "c-proportion-redistributed"     ~ "Proportion redistributed",
      param == "c-toilet-cleaning-rate"         ~ "Toilet cleaning rate",
      param == "c-toilet-cleaning-effect"       ~ "Toilet cleaning effect",
      TRUE                                      ~ param
    )
  ) %>% 
  ggplot(aes(x = value, y = mean_cases)) + 
  geom_line() + 
  geom_ribbon(aes(ymin = mean_cases - sd_cases, ymax = mean_cases + sd_cases), alpha = 0.2) +
  facet_wrap(~ param, scales = "free") +    # free_x required to use facetted_pos_scales
  # apply percentage labels and a per-facet x-title only for the antibiotic facet
  ggh4x::facetted_pos_scales(
    x = list(
      # LHS is evaluated against the facet layout; RHS is the scale to use for matching facets
      param %in% c("Antimicrobial prescription rate", "Proportion redistributed", "Toilet cleaning effect") ~
        scale_x_continuous(
          labels = scales::label_percent(scale = 100)   # data already on 0-100 so use scale=1
        )
    )
  ) +
  # fallback labels (these apply to facets that did not get a custom scale)
  labs(x = "Parameter value",
       y = "Number of infected patients")
```

>>>>

param_units <- c("toilet-frequenting-rate" = "times per day",
                 "toilet-cleaning-rate" = "times per day",
                 "toilet-contamination-effect" = "",
                 "toilet-cleaning-effect" = "",
                 "community-colonisation-rate" = "percentage of patients",
                 "antibiotic-prescription-rate" = "percentage of admissions",
                 "antibiotic-effect" = "relative risk",
                 "random-colonisation" = "cases per 10,000 bed days",
                 "side-room-delay-mean" = "days")

param_names <- c("toilet-frequenting-rate" = "Toilet frequenting rate",
                 "toilet-cleaning-rate" = "Toilet cleaning rate",
                 "toilet-contamination-effect" = "Toilet contamination effect",
                 "toilet-cleaning-effect" = "Toilet cleaning effect",
                 "community-colonisation-rate" = "Community colonisation rate",
                 "antibiotic-prescription-rate" = "Antibiotic prescription rate",
                 "antibiotic-effect" = "Antibiotic effect",
                 "random-colonisation" = "Random colonisation",
                 "side-room-delay-mean" = "Side room delay mean")

@@

```{r fig-sensitivity-analysis, include=TRUE, eval=TRUE}
#| echo: false
#| fig-cap: "Sensitivity analysis of the model to changes in key infection control parameters. The y axis shows the total number of nosocomial infections during the outbreak period. Antimicrobial prescription rate represents the percentage of patients that were administered an antimicrobial during their admission. Proportion redistributed represents the proportion of infected patients that were moved to a single-occupancy room (lower values represent fewer patients being moved). Toilet cleaning effect represents the effectiveness of cleaning in reducing toilet contamination (100% = complete removal of contamination; 0% = no cleaning effect). Toilet cleaning rate represents the number of times toilets were cleaned per day, on average."
list(
  abx_prescription_rate    = sens_abx_prescription_outbreak_cases,
  proportion_redistributed = sens_prop_redist_outbreak_cases,
  toilet_cleaning_rate     = sens_toilet_cleaning_rate_outbreak_cases,
  toilet_cleaning_effect   = sens_toilet_cleaning_effect_outbreak_cases
) %>%
  bind_rows() %>% 
  pivot_longer(
    cols = starts_with("c-"),
    names_to = "param",
    values_drop_na = TRUE
  ) %>% 
  group_by(param, value) %>% 
  summarise(
    mean_cases = mean(`outbreak-cases`),
    sd_cases   = sd(`outbreak-cases`),
    .groups    = "keep"
  ) %>% 
  mutate(
    # convert antibiotic prescription rate to 0-100 scale, leave others unchanged
    # value = if_else(param == "c-antibiotic-prescription-rate", value * 100, value),
    param = case_when(
      param == "c-antibiotic-prescription-rate" ~ "Antimicrobial prescription rate",
      param == "c-side-room-delay-mean"     ~ "Side room delay mean",
      param == "c-toilet-cleaning-rate"         ~ "Toilet cleaning rate",
      param == "c-toilet-cleaning-effect"       ~ "Toilet cleaning effect",
      TRUE                                      ~ param
    )
  ) %>% 
  ggplot(aes(x = value, y = mean_cases)) + 
  geom_line() + 
  geom_ribbon(aes(ymin = mean_cases - sd_cases, ymax = mean_cases + sd_cases), alpha = 0.2) +
  facet_wrap(~ param, scales = "free") +    # free_x required to use facetted_pos_scales
  # apply percentage labels and a per-facet x-title only for the antibiotic facet
  ggh4x::facetted_pos_scales(
    x = list(
      # LHS is evaluated against the facet layout; RHS is the scale to use for matching facets
      param %in% c("Antimicrobial prescription rate", "Proportion redistributed", "Toilet cleaning effect") ~
        scale_x_continuous(
          labels = scales::label_percent(scale = 100)   # data already on 0-100 so use scale=1
        )
    )
  ) +
  # fallback labels (these apply to facets that did not get a custom scale)
  labs(x = "Parameter value",
       y = "Number of infected patients")
```
